\hrule\hrule\bigskip\bigskip A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum games with imcomplete information

### 2015-06-07 nips2015.tex
giving credits

\subsection{Relaxing the conditions for equilibrium}
Let us first introduce the notion of $\epsilon$-subgradients.

@@

Henceforth, the notion of approximate Nash equilibria will be
understood in the following sense.

>>>>

\subsection{Relaxing the conditions for equilibrium}
Let us first introduce the notion of $\epsilon$-subgradients
\cite{he2013accelerating}.

@@

Henceforth, the notion of approximate Nash equilibria will be
understood in the following sense, which was first introduced in
\cite{he2013accelerating}.
